Stool Microbiome Analysis

### 2021-12-08 Rmarkdown/analysis/Fecal_Microbiome_TMAO_Analysis_211105.Rmd
Exploratory analysis to determine differentiating b-diversity factor visible in plots

>>>>

Play around with the coloring to try to figure out what is discriminating these groups!

```{r What defines the PCoA groups exploration}
colnames(sample_data(PSOtmao1G))
loopPheno <- c("pa_ee_total_mdn","endo_ln_rhi_mdn", "endo_al75_mdn", "betaine_mdn", "carnitine_mdn", "tmao_mdn",  "choline_mdn", "creatinine_mdn", "phosphocholine_mdn", "hei_asa24_totalveg_mdn", "hei_asa24_totalproteinfoods_mdn", "hei_asa24_sodium_mdn", "hei_asa24_refinedgrains_mdn", "hei_asa24_sfat_mdn",  "hei_asa24_addsug_mdn", "hei_asa24_wholegrain_mdn", "hei_asa24_totalscore_mdn", "tmao_log_mdn", "TMAO_5", "TMAO_6", "TMAO_7", "sex", "age_cat", "bmi_cat", "tmao_quantile", "tmao_tertile")

# PCoA_WU, PCoA_UnWU, PCoA_BC plug in to view
for(i in 1:length(loopPheno)){
print(plot_ordination(PSOtmao1G, PCoA_WU, 
                    color = loopPheno[i],
                    shape = NULL,
                    axes = 1:2) +
  #scale_color_brewer(palette = "Dark2", labels = c("Below", "Above")) +
  stat_ellipse(linetype = 1) +
  labs(color = loopPheno[i]) +
  theme_minimal() + 
  theme(axis.text = element_text(size = 12), # x and y axis text size
        axis.title = element_text(size = 12), # x and y label text size
        legend.text = element_text(size = 12), # legend text size
        legend.title = element_text(size = 12), # label legend text size
        axis.text.x = element_text(angle = -90, hjust = 0, vjust=0.5)))
}

# From the plots, Weighted UniFrac and endo_al75 and betaine look different
bdis <- betadisper(dismax_wu, df$betaine_mdn)
permutest(bdis) # NS, good
boxplot(bdis, las = 2)

# ADONIS (perMANOVA) analysis
adonis2(dismax_wu ~ betaine + sex + age + bmi_final.y, data=df, method = "wunifrac", perm=999) # different
